EWJN from a BCS Superconductor

### 2021-02-05 paper.tex
Adds logarithm branch cut
Adds figure calcs

The dielectric function $\epsilon(q, \omega)$, then, contains the information needed to describe the electromagnetic properties of the surface near the qubit.
For the normal state, the dielectric function derived by Lindhard~\cite{Lindhard} used in~\cite{QubitRelax} describes the non-local electromagnetic response of a metal.
Using the form described by Solyom\cite{SolyomV3},
\begin{equation}
	\epsilon_{\mathrm{Lindhard}}(\vec{q}, \omega) = 1 + \frac{q_{TF}^2}{q^2}\frac{\displaystyle 1 + \frac{\omega + \flatfrac{i}{\tau}}{2 \vf q} \ln(\frac{\omega - \vf q + \flatfrac{i}{\tau}}{\omega + \vf q + \flatfrac{i}{\tau}})}{\displaystyle 1 + \frac{\flatfrac{i}{\tau}}{2 \vf q} \ln(\frac{\omega - \vf q + \flatfrac{i}{\tau}}{\omega + \vf q + \flatfrac{i}{\tau}})}. \label{eq:lindhardsolyom}
\end{equation}
Here, $q_{TF}$ is the Thomas-Fermi wavevector $q_{TF}^2 = 3 \flatfrac{\omega_p^2}{\vf^2}$, $\omega_p$ is the plasma frequency $\sqrt{\flatfrac{4 \pi n e^2}{m}}$, $\tau$ is the collision time and $\vf$ is the Fermi velocity.
This can be shown to reduce to the Drude dielectric function in the $q \rightarrow 0$ limit.

The Lindhard dielectric function reflects the important property of having an imaginary part that vanishes for $q$ such that $\abs{\varepsilon_q - \omega} >  q\vf$.
This is a very generic feature of these types of response functions, and occurs because there are no points on the assumed spherical Fermi surface further than $2 q_{\mathrm{F}}$ apart.
Thus, there are no available quasiparticle-hole excitations available for energy dissipation (cf discussion in \cite{AGD}, \cite{FetterWalecka} or \cite{SolyomV3}).
This is a general argument, and it should be expected that a superconducting dielectric function should also have zero imaginary part above some momentum on the order of the Fermi momentum.
Because the Lindhard dielectric function's imaginary part vanishes above a cutoff $q_c\left(\omega\right)$ and has real part that goes as $\frac{1}{q^2}$, all of the integrals in $\eqref{eq:chi}, \eqref{eq:zp} and \eqref{eq:zs}$ converge.

>>>>

The dielectric function $\epsilon(q, \omega)$, then, contains the information needed to describe the electromagnetic properties of the surface near the qubit.
For the normal state, the dielectric function derived by Lindhard~\cite{Lindhard} used in~\cite{QubitRelax} describes the non-local electromagnetic response of a metal.
Using the form described by Solyom\cite{SolyomV3},
\begin{equation}
	\epsilon_{\mathrm{Lindhard}}(\vec{q}, \omega) = 1 + \frac{q_{TF}^2}{q^2}\frac{\displaystyle 1 + \frac{\omega + \flatfrac{i}{\tau}}{2 \vf q} \ln(\frac{\omega - \vf q + \flatfrac{i}{\tau}}{\omega + \vf q + \flatfrac{i}{\tau}})}{\displaystyle 1 + \frac{\flatfrac{i}{\tau}}{2 \vf q} \ln(\frac{\omega - \vf q + \flatfrac{i}{\tau}}{\omega + \vf q + \flatfrac{i}{\tau}})}. \label{eq:lindhardsolyom}
\end{equation}
Here, $q_{TF}$ is the Thomas-Fermi wavevector $q_{TF}^2 = 3 \flatfrac{\omega_p^2}{\vf^2}$, $\omega_p$ is the plasma frequency $\sqrt{\flatfrac{4 \pi n e^2}{m}}$, $\tau$ is the collision time and $\vf$ is the Fermi velocity.
The branch cut for the logarithm is chosen here such that their imaginary parts lie between $\pm i \pi$.
This can be shown to reduce to the Drude dielectric function in the $q \rightarrow 0$ limit.

The Lindhard dielectric function reflects the important property of having an imaginary part that vanishes for $q$ such that $\abs{\varepsilon_q - \omega} >  q\vf$.
This is a very generic feature of these types of response functions, and occurs because there are no points on the assumed spherical Fermi surface further than $2 q_{\mathrm{F}}$ apart.
Thus, there are no available quasiparticle-hole excitations available for energy dissipation (cf discussion in \cite{AGD}, \cite{FetterWalecka} or \cite{SolyomV3}).
This is a general argument, and it should be expected that a superconducting dielectric function should also have zero imaginary part above some momentum on the order of the Fermi momentum.
Because the Lindhard dielectric function's imaginary part vanishes above a cutoff $q_c\left(\omega\right)$ and has real part that goes as $\Re \epsilon_{\mathrm{Lindhard}} - 1 \sim \frac{1}{q^2}$, all of the integrals in $\eqref{eq:chi}, \eqref{eq:zp} and \eqref{eq:zs}$ converge.
